High resolution, annual maps of the characteristics of smallholder-dominated croplands at national scales

### 2021-07-01 inst/manuscript/si.Rmd
Methods reorganization complete

documentclass: article
classoption: a4paper
capsize: normalsize
fontsize: 11pt
geometry: margin=1in
linenumbers: yes
spacing: doublespacing
# abstract: The abstract can go either here or below
keywords: rmarkdown, reproducible science
bibliography: 
  - references.bib
  - knitcitations.bib
csl: ecology.csl

@@

## Composites Assessing quality of composites
The rubric presented in Table \ref{tab:imqcriteria} was used to assess the quality of the seasonal image composites. The imagery was evaluated by examining their Raster Foundry [@azaveaRasterFoundry2020] overlays within a `labeller` instance set up for the purpose.

@@

Two supervisors (Ye and Estes) who were not involved in labelling developed the map reference sample evaluated the PlanetScope composites at each site to determine its class membership. The following set of rules were followed in collecting the sample:

>>>>

documentclass: article
classoption: a4paper
capsize: normalsize
fontsize: 11pt
geometry: margin=1in
linenumbers: yes
spacing: doublespacing
# abstract: The abstract can go either here or below
keywords: rmarkdown, reproducible science
bibliography: 
  - references.bib
csl: ecology.csl

@@

## Assessing quality of composites
The rubric presented in Table \ref{tab:imqcriteria} was used to assess the quality of the seasonal image composites. The imagery was evaluated by examining their Raster Foundry [@azaveaRasterFoundry2020] overlays within a `labeller` instance set up for the purpose.

@@

Two supervisors (Ye and Estes), who were not involved in collecting training and validation labels, collected the map reference sample by evaluating the PlanetScope composites at each site to determine its class membership. The following set of rules were followed in collecting the sample:
